Towards human SuperEEG

### 2018-10-05 paper/main.tex

We first examined held-out raw LFP traces and their associated
SuperEEG-derived reconstructions.  Figure~\ref{fig:recon}A displays
the observed LFP from the red electrode in Figure~\ref{fig:methods}A
(red), and its associated reconstruction (black), during a 5~s time
window during one of the example patient's six recording sessions.
The two traces match closely ($r = XXX, p = XXX$).  Where the traces
do not align, the predicted trace tends to be rounded towards zero,
reflecting the zero-mean prior implicit in
Equation~\ref{eqn:reconstruction} (paired $t$-test comparing absolute
values of actual versus predicted voltages: $t(XXX) = XXX, p = XXX$).

\textbf{JRM STOPPED HERE}
% JRM thoughts:
% - Tie in stats from supplemental analyses.  Fig S4: total number of
% electrodes, total number of used electrodes, prop thresholded, total
% recording time, average session time, number of sessions.

Figure~\ref{fig:recon}B displays a two-dimensional histogram of the
actual versus reconstructed voltages for every sample across 14.2
total hours of recordings from that patient (correlation:
$r = 0.91, p < 10\textsuperscript{-10}$).  Although the SuperEEG
algorithm recovered the recordings from this electrode well, we sought
to quantify the algorithm's performance across the full dataset.

%sample trace & reconstruction, several frames of activity snapshot?
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/recon}
  \caption{\textbf{Observed and reconstructed LFP from a single
      electrode.} \textbf{A. Example LFP.}  A 2~s recording from the blue
    electrode in Figure~\ref{fig:methods}A is displayed in red, and
    the reconstructed LFP during the same time window is shown in
   black.  All voltages are plotted in standard deviation units.
    \textbf{B. Observed versus reconstructed voltages over 14.2~hours.}
    The 2D histogram reflects the relation between distributions of
    observed versus reconstructed voltages from one patient, across the
    14.2 hours of recorded data collected in 6 recording sessions.  The
    correlation reported in the panel is between the observed and reconstructed
    voltages.}
  \label{fig:recon}
\end{figure}

>>>>

We first examined individual held-out raw LFP traces and their
associated SuperEEG-derived reconstructions.  Figure~\ref{fig:recon}A
displays the observed LFP from the red electrode in
Figure~\ref{fig:methods}A (red), and its associated reconstruction
(blue), during a 5~s time window during one of the example patient's
six recording sessions.  The two traces match closely
($r = XXX, p = XXX$).
%Where the traces do not align, the predicted
%trace tends to be rounded towards zero, reflecting the zero-mean prior
%implicit in Equation~\ref{eqn:reconstruction} (paired $t$-test
%comparing absolute values of actual versus predicted voltages:
%$t(XXX) = XXX, p = XXX$).
Figure~\ref{fig:recon}B displays a
two-dimensional histogram of the actual versus reconstructed voltages
for the entire 14.2 total hours of recordings from the electrode
(correlation: $r = XXX, p = XXX$).
%Like in the shorter example trace
%shown in panel A, the reconstructed voltages throughout the full
%recording tended to be smaller in magnitude than the original
%recording ($t(XXX) = XXX, p = XXX$).
Having confirmed that the SuperEEG algorithm recovered the recordings
from this electrode well, we next sought to quantify the algorithm's
performance across the full dataset.

%sample trace & reconstruction, several frames of activity snapshot?
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/recon}
  \caption{\textbf{Observed and reconstructed LFP from a single
      electrode.} \textbf{A. Example LFP.}  A 5~s recording from the
    red electrode in Figure~\ref{fig:methods}A is displayed in red,
    and the reconstructed LFP during the same time window is shown in
    blue.  \textbf{B. Observed versus reconstructed voltages over
      14.2~hours.}  The two-dimensional histogram reflects the
    relation between distributions of observed versus reconstructed
    voltages from one patient, across the 14.2 hours of recorded data
    collected over 6 recording sessions.  The correlation reported in
    the panel is between the observed and reconstructed voltages.
    Both panels: all voltages are represented in standard deviation units
   (computed within session).}
  \label{fig:recon}
\end{figure}
